Tactic Script Optimisation for Aesop

### 2024-09-10 paper.tex
Improve algorithm notation
... following Jasmin's suggestions.

\begin{algorithm}
  \begin{algorithmic}
    \Function{reorder-static}{$\mathit{steps}$}
      \If{$\mathit{steps}$ is empty}
        \State \Return $[]$
      \EndIf
      \State \Let $g$ be the pre-goal of the first step
      \State $\mathit{tacticState} \gets [g]$
      \State $r \gets []$
      \While{$\mathit{tacticState}$ contains at least one goal}
        \State $\mathit{step} \gets \Call{next-step}{\mathit{tacticState}, \mathit{steps}}$
        \State $\mathit{tacticState} \gets \Call{apply-step}{\mathit{tacticState}, \mathit{step}}$
        \State Append $\mathit{step}$ to $r$
      \EndWhile
      \State \Return $r$
    \EndFunction

@@

    \Function{next-step}{$\mathit{tacticState}, \mathit{steps}$}
      \State \Let $g$ be the first goal in $\mathit{tacticState}$
      \If{$g$ does not contain metavariables}
        \State \Return the step for $g$
      \Else
        \State \Return the first step whose pre-goal is contained
        \State \hspace{\widthof{\Return}} \cindent in $\mathit{tacticState}$
      \EndIf
    \EndFunction

@@

    \Function{apply-step}{$\mathit{tacticState}, (Φ, g, t, Ψ, G)$}
      \State \Let $\mathit{tacticState}$ be $[g₁, \dots, gₙ, g, h₁, \dots, hₘ]$
      \State \Let $G$ be $[k₁, \dots, kₗ]$
      \State $r \gets [g₁, ..., gₙ, k₁, \dots, kₗ, h₁, \dots, hₘ]$
      \State Remove from $r$ each goal $x$ such that $x$ is assigned in
      \State \cindent $Ψ$ but not in $Φ$
      \State \Return $r$
    \EndFunction
  \end{algorithmic}
  \caption{Static reordering}\label{alg:static-reordering}
\end{algorithm}

@@

    \Function{apply-step}{$\mathit{steps}, Φ, G, g, s$}
      \State \Let step $s$ be $(Φ^{\pre}, g, t, Φ^{\post}, G^{\post})$
      \State Run $t$ in tactic state $(Φ, [g])$, producing tactic state
      \State \cindent $(Ψ, G')$
      \If{$(Φ^{\post}, G^{\post}) \aeq (Ψ, G')$}
        \State \Let $σ$ be the partial map from metavariables in $Φ^{\post}$
        \State \hspace{\widthof{\Let}} \cindent to matching metavariables in $Ψ$
        \State For each step in $\mathit{steps}$, replace its pre-goal $g^{\pre}$
        \State \cindent with $σ(g^{\pre})$ if $g^{\pre} ∈ \dom(σ)$
        \State $s' \gets (Φ, g, t, Ψ, G')$
        \State \Let $G$ be $[g₁, \dots gₙ, g, k₁, \dots, kₘ]$
        \State \Let $G'$ be $[h₁, \dots, hₗ]$
        \State $H \gets [g₁, \dots, gₙ, h₁, \dots, hₗ, k₁, \dots, kₘ]$
        \State Remove from $H$ each goal that is assigned in $Ψ$
        \State $(\mathit{script}, Ω) \gets \Call{reorder-dynamic}{\mathit{steps}, Ψ, H}$
        \State \Return $(s' ∷ \mathit{script}, Ω)$
      \Else
        \State \Failure
      \EndIf
    \EndFunction
  \end{algorithmic}
  \caption{Dynamic reordering}\label{alg:dynamic-reordering}
\end{algorithm}

>>>>

\begin{algorithm}
  \begin{algorithmic}
    \Function{reorder-static}{$\mathit{steps}$}
      \If{$\mathit{steps}$ is empty}
        \State \Return $[]$
      \EndIf
      \State \Let $g$ be the pre-goal of the first step in $\mathit{steps}$
      \State $\mathit{tacticState} \gets [g]$
      \State $r \gets []$
      \While{$\mathit{tacticState}$ contains at least one goal}
        \State $\mathit{step} \gets \Call{next-step}{\mathit{tacticState}, \mathit{steps}}$
        \State $\mathit{tacticState} \gets \Call{apply-step}{\mathit{tacticState}, \mathit{step}}$
        \State Append $\mathit{step}$ to $r$
      \EndWhile
      \State \Return $r$
    \EndFunction

@@

    \Function{next-step}{$\mathit{tacticState}, \mathit{steps}$}
      \State \Let $g$ be the first goal in $\mathit{tacticState}$
      \If{$g$ does not contain metavariables}
        \State \Return the step for $g$ from $\mathit{steps}$
      \Else
        \State \Return the first step from $\mathit{steps}$ whose pre-goal is
        \State \hspace{\widthof{\Return}} \cindent contained in $\mathit{tacticState}$
      \EndIf
    \EndFunction

@@

    \Function{apply-step}{$\mathit{tacticState}, (Φ, g, t, Ψ, G)$}
      \State \Let $G$ be $[g₁, \dots, gₙ]$
      \State Replace $g$ with $g₁, \dots, gₙ$ in $r$
      \State Remove from $r$ each goal $g'$ such that $g'$ is assigned in
      \State \cindent $Ψ$ but not in $Φ$
      \State \Return $r$
    \EndFunction
  \end{algorithmic}
  \caption{Static reordering}\label{alg:static-reordering}
\end{algorithm}

@@

    \Function{apply-step}{$\mathit{steps}, Φ, G, g, s$}
      \State \Let step $s$ be $(Φ^{\pre}, g, t, Φ^{\post}, G^{\post})$
      \State Run $t$ in tactic state $(Φ, [g])$, producing tactic state
      \State \cindent $(Ψ, G')$
      \If{$(Φ^{\post}, G^{\post}) \aeq (Ψ, G')$}
        \State \Let $σ$ be the partial map from metavariables in $Φ^{\post}$
        \State \hspace{\widthof{\Let}} \cindent to matching metavariables in $Ψ$
        \State For each step in $\mathit{steps}$, replace its pre-goal $g'$ with
        \State \cindent $σ(g')$ if $g' ∈ \dom(σ)$
        \State $s' \gets (Φ, g, t, Ψ, G')$
        \State \Let $G'$ be $[g₁, \dots, gₙ]$
        \State Replace $g$ with $g₁, \dots, gₙ$ in $G$
        \State Remove from $G$ each goal that is assigned in $Ψ$
        \State $(\mathit{script}, Ω) \gets \Call{reorder-dynamic}{\mathit{steps}, Ψ, G}$
        \State \Return $(s' ∷ \mathit{script}, Ω)$
      \Else
        \State \Failure
      \EndIf
    \EndFunction
  \end{algorithmic}
  \caption{Dynamic reordering}\label{alg:dynamic-reordering}
\end{algorithm}
